Initial Analysis

### 2020-08-07 Scripts/Initial_Analysis.Rmd
Cleaned script for reviewers

## Determine Species Status

@@

@@

# Percentage species analyzed from the identified species
936/length(unique(SAU_Global_Data$taxon_key))

@@

# Read SAU non-reconstructed catch data from 2006 for comparrisonwith Sumaila
# Provided by Vicky Lam
SAU_FAO_Data <- fread(paste(my_path("D"),"Distribution/LVCatch_byYrEEZFETaxa_2010_14.csv", sep ="")) %>% 
  filter(#eezid != 0,
         year == 2006) %>%
  group_by(fishing_entity_id,taxon_key,eezid) %>% 
  summarise_at(c("sumcatch"),
               sum,na.rm=T)

SAU_FAO_Data_a <- fread(paste(my_path("D"),"Distribution/LVCatch_byYrEEZFETaxa_2010_14.csv", sep =""))
SAU_FAO_Datab <- fread(paste(my_path("D"),"Distribution/LVCatch_byYrEEZFETaxa_2005_09.csv", sep =""))

# FAO data
total_FAO_catch <- bind_rows(SAU_FAO_Data_a,SAU_FAO_Datab) %>% 
  filter(eezid != 0) %>% 
  group_by(fishing_entity_id,taxon_key,eezid) %>% 
  summarise(mean_c = mean(sumcatch,na.rm=T)) %>% 
  group_by() %>% 
  summarise_at(vars(mean_c),sum)

total_sampled_FO_catch <- bind_rows(SAU_FAO_Data_a,SAU_FAO_Datab) %>% 
  filter(eezid != 0) %>% 
  filter(taxon_key %in% Species_Sampled$TaxonKey) %>% 
  group_by(fishing_entity_id,taxon_key,eezid) %>% 
  summarise(mean_c = mean(sumcatch,na.rm=T)) %>% 
  group_by() %>% 
  summarise_at(vars(mean_c),sum)

SAU_FAO_Data %>% 
  filter(taxon_key %in% Species_Sampled$TaxonKey) %>%
  group_by() %>% 
  summarise(sum(sumcatch))

@@

@@

### Discrete Exclusive

@@

### Data For Map

@@

### EEZ Map of Transboundary Species

@@

  Rev_Plot <- ggplot(
    # Regional plots
    data = Subregion_Rev_Data,
    aes(
      x=reorder(id,Value_sum),
      y=Value_sum, 
      fill=Value_sum
    )
  ) +    
    ylim(-5, 30) +
    geom_bar(stat="identity") +
    # Regional averages
    geom_point(data = Subregion_Rev_Data,
               aes(
                 x=reorder(id,Value_sum),
                 y=Value_m
               ),
               colour = "black",
               alpha = 0.5,
               size = 0.5
    ) +
    # Regional sds
    geom_errorbar(data = Subregion_Rev_Data,
                  aes(
                    ymin=ifelse(Value_m-Value_sd <= 0,0,Value_m-Value_sd), # sets lower to 0
                    ymax=Value_m+Value_sd
                  ), 
                  width=.2,
                  position=position_dodge(.9),
                  alpha = 0.5) +
    # Looking good
    theme_minimal(base_size = 9) +
    theme(
      legend.key.width =unit(1,"line"),
      legend.key.height =unit(0.9,"line"),
      legend.position = c(0.86,0.55),
      axis.text = element_blank(),
      axis.title = element_blank(),
      panel.grid = element_blank(),
      plot.margin = margin(1,0,0,-2.5,"cm") # top,x,x,left
      # plot.margin = margin(0,-10,-6,-10,"cm")
    )  +
  coord_polar(start = 0) + 
  geom_text(data=label_data_rev, 
            aes(x=id,
                # y=ifelse(sub_region=="N. Europe",250,Value_sum+1), # Fix names overlap
                y = Value_sum,
                label=sub_region,
                hjust=hjust), 
            color="black",
            fontface="bold",
            size=2, 
            angle= label_data_rev$angleb, 
            inherit.aes = FALSE) +
    scale_fill_gradientn("",
                         colours = pal,
                         limits = c(0,30),
                         breaks = seq(0,30,6)
                         ) + # puts legend text on the left
    guides(fill = guide_colorbar(label.position = "left"));Rev_Plot

@@

### OHI-inspired Circular plot for Territories

@@

### Mackerel (*Scomber scombrus*) war

@@

### OHI-inspired Circular plot Species

@@

#Problem solving

### First world Anchovies

In a first run the model suggests anchovies "Engraulis ringens" (600004) is transboundary between US-Mex-Can. I'm exploring this since all four models agree...

Found the problem, Gab's coordinate system, hence the data, are in different system than DBEM and SAU data...

```{r Trans_Spp_Function, eval= F ,echo = T,warning = F,message = F}

### DATA EXTRA NEEDED

# DBEM Coordinate system
Coor <- fread(paste(Data_Path,"Spatial_Data/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
colnames(Coor) <- c("INDEX","Longitude","Latitude")
EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
colnames(EEZ_CellID) <- c("EEZID","INDEX")

# colnames(CoorG) <- c("INDEX","Longitude","Latitude")
coords <- CoorG[order(CoorG$Latitude, rev(CoorG$Longitude),decreasing=TRUE), ]

# Explore model step by step

# Get Catch Data
Anchoveta_Dist <- GetSppDist(600004,"All",CoorG)

Anchoveta_Dist_Coor <- Anchoveta_Dist %>% 
  left_join(CoorG)

# Swap coordinate system to match DBEM and SAU
Anchoveta_Dist_Coor_Fix <- Anchoveta_Dist_Coor[order(Anchoveta_Dist_Coor$Latitude, rev(Anchoveta_Dist_Coor$Longitude),decreasing=TRUE), ]

x <- Anchoveta_Dist %>% 
  left_join(EEZ_CellID) %>% 
  left_join(EEZIDs_List) %>% 
  filter(
    # Model == "Occ",
    Value >0)

# head(x)
# Exploring using Vicky's data

ggplot(x) +
  geom_tile(aes(
    x = Longitude,
    y = Latitude,
    fill = Name,
    color = Name
  )
  ) +
  facet_wrap(~Model)

Spp_Trans <- bind_rows(
  mclapply(
    600004, FUN =EstTransIndex, Model = "All", Neighbours = Neighbour_List, Coord = CoorG
  )
)

# Estimate total spp distribution within neighbours

Trans_Spp <- SppDist %>%
  filter(INDEX %in% Neighbours$INDEX) %>% # Filter data only located within EEZs
  mutate(Value = ifelse(Value > 0, 1,0)) %>%  # For now using SAU_C as presence absence
  group_by(TaxonKey,
           INDEX
  ) %>%
  summarise(Model_Index = mean(Value,na.rm=T)) %>%
  filter(Model_Index > 0) %>%
  mutate(Model_Index = Model_Index*100) %>%
  left_join(Neighbours,
            by = "INDEX")

Test <- Trans_Spp %>% 
  filter(Name == "USA (West Coast)" & Model_Index ==100)

# Explore only SAU catch data

# Get Catch Data
Anchoveta_Dist <- GetSppDist(Spp,"SAU_C")

# Get Mex, Can and USA W coast Grid
Anchoveta_Dist_EEZ <- Anchoveta_Dist %>%

  Anchoveta_NA <-  Anchoveta_Dist%>% 
  filter(INDEX %in% North_America$INDEX) %>% 
  gather("Year","Tonnes",CATCH.1:CATCH.65) %>% 
  group_by(Year) %>% 
  summarise(Sum_T = sum(Tonnes, na.rm =T))

### Over-counting transboundary stocks

In a first run, Australia results in many transboundary stocks, I believe this is because it is counting the number of countries that that the species share (e.g. one species 6 countries = 6 transboundary spp) rather than 1 species 6 countries = 1 trans spp.

**Problem fixed.** Now we can estimate the number of transboundary species as well as the number of countries/regions that each country shares per species.

```{Australia_case, eval =F, echo = F}

Australia <- Results_Data %>% 
  filter(Name == "Australia")

Original_Australia <-Australia %>% 
  filter(Model_Index >= 50#,
         # Trans_Index >= 0.10
  ) %>% 
  group_by(Name,Model_Index) %>% 
  summarise(n_Trans_Spp = n()) %>% 
  filter(Model_Index == 100)

## Testing the waters

Explore_Australia <- Australia %>% 
  filter(Model_Index >= 50#,
         # Trans_Index >= 0.10
  ) %>% 
  slice(1:20) %>% 
  group_by(Name,Model_Index) %>% 
  summarise(
    n_trans = length(unique(TaxonKey)),
    n_countries = length(unique(Neighbour_Territory)),
  )

### Fixing counts within EEZs

In the first run. Countries where EEZs are divided but touching (e.g. South Africa Indian and Atlantic coasts) are double counted.

This might be fixed with Tyler's data of EEZs to ISOs... He did it manually so it does not work!

```{South_Africa_case, eval =F, echo = F}

# Tyler E.'s' data
EEZ_ISO <- read.csv("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Spatial_Data/EEZID_ISO_TylEd.csv", comment.char="#")

#SAU / Vicky's data
EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))

EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
colnames(EEZ_CellID) <- c("EEZID","INDEX")

# Worlds adata

# The path
path_world <- paste(Data_Path,"Spatial_Data/World_EEZ_v10_2018",sep="")
# #The File
fnam_world <- "eez_v10.shp"
# #Load it!
# 
World_EEZs <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world))

head(World_EEZs)

World_EEZs %>% 
  filter(
    # Territory1 == "South Africa",
    ISO_Ter1 == "ZAF") %>% 
  head()

# Get ISO and territory names from world map
ISO_Ter <- World_EEZs %>%
  select(ISO_Ter1,Territory1) %>% 
  as.data.frame() %>% 
  select(ISO_Ter1,Territory1)

head(ISO_Ter)

# I think EEZID equals ISO when not devided...

EZZID_Yes_ISO <- ISO_Ter %>% 
  semi_join(ISO_Ter,
            by ="ISO_Ter1") %>% 
  rename(Name = Territory1) %>% 
  # head() %>% 
  left_join(EEZIDs_List,
            by = "Name")

EEZ_ISO_Clean <- ISO_Ter %>% 
  left_join(EEZ_ISO,
            by = "ISO_Ter1")

SA <- Results_Data %>% 
  filter(stringr::str_detect(Name,"South Africa"))

## Creating a subset dataset so i can work on my laptop and not remoteley

SubsetData <- Clean_Results %>% 
  filter(Country_Territory=="USA (East Coast)")

write.csv(SubsetData,
          "SubsetData.csv",
          row.names = F) # Using USA East coast and Gulf as example

###_____________________________ ###

# Loading subsetted data

Clean_Results <- read.csv("~/GitHub/FishForVisa/Temporal_Data/SubsetData.csv")

sau_eez_fes <- read.csv("~/GitHub/FishForVisa/Temporal_Data/sau_eez_fes.csv")

Neighbourd_Territory_T <- Clean_Results %>% 
  group_by(eez_name=Neighbour_Territory) %>% 
  summarise() %>%
  left_join(sau_eez_fes,
            by = "eez_name") %>% 
  select(Neighbour_Territory= eez_name,
         NT_fishing_entity=fishing_entity
  )

Country_Territory_T <- Clean_Results %>% 
  group_by(eez_name=Country_Territory) %>% 
  summarise() %>%
  left_join(sau_eez_fes,
            by = "eez_name")  %>% 
  select(Country_Territory= eez_name,
         CT_fishing_entity=fishing_entity)

Non_duplicate_Data <- Clean_Results %>%   
  left_join(Neighbourd_Territory_T,
            by ="Neighbour_Territory") %>% 
  left_join(Country_Territory_T,
            by ="Country_Territory") %>% 
  mutate(
    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
  ) %>% 
  filter(Same_Nation == "No")

# FIXED!!!!!

- **Done debugging**

### Missing stocks

There are places like Peru-Chile or Alaska-Canada that should have trans spp... In Alaska the issue is that Alaska doesn't actually exist as a separate shapefile...

```{r Missing_stocks, eval =F}

Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/exploited_species_list.csv",sep=""))

Clean_sau_eez_fes <- sau_eez_fes %>% 
  gather("Type","FishingRegion",2,4) %>% 
  left_join(sau_eez_fes,
            by = ("fishing_entity_id")
  ) %>% 
  group_by(FishingRegion,fishing_entity) %>% 
  summarise(n())

# The Alaska paradox
# It's a problem of the NAs, fixed.

USA_West <- Results_Data %>% 
  filter(Country_Territory == "USA (West Coast)") %>% 
  left_join(Exploited_Species,
            by = "TaxonKey")

# Northern sea Russia
Russia_map <- World_EEZs %>% 
  filter(stringr::str_detect(Name,"Russia")) %>% 
  st_simplify(preserveTopology = TRUE, dTolerance = 100)

head(Russia_map)

ggplot(Russia_map) +
  geom_sf(aes(fill = Name)) 
# Shapefiles not matching
# Russia (Laptev to Chukchi Sea)
# Russia (Kara Sea)

Russian_Regions <- c("Russia (Laptev to Chukchi Sea)","Russia (Kara Sea)")

Russia_Results <- Results_Data %>% 
  filter(stringr::str_detect(Country_Territory,"Russia"))

unique(Russia_Results$Country_Territory)
# Missing Laptev to Chukchi sea

### What about Vicky's data
#SAU / Vicky's data
EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))

Russia_EEZlist <- EEZIDs_List %>% 
  filter(stringr::str_detect(Name,"Russia"))

unique(Russia_EEZlist$Name)

### So maybe there are no Neighbours?
Neighbour_List <- fread(paste(Data_Path,"Spatial_Data/Neighbour_List.csv", sep =""))

Russia_Neighbour <- Neighbour_List %>% 
  filter(stringr::str_detect(Name,"Russia"))

unique(Russia_Neighbour$Country_Territory)

# OK So Kara Sea has no borders outside Russia, hence white. Now Laptev does have borders but No species... which is weird... Paific Halibut?

# I manually ran the function to see what's going on

# ggplot() +
#   geom_sf(data = Russia_map, aes(colour = Name)) +
#   geom_tile(data = subset(SppDist, Value !=0),
#             aes(
#     x = Longitude,
#     y = Latitude,
#     fill = log10(Value)
#   ) 
#   ) +
#   facet_wrap(~Model)

# The main issue is that there is no catch data there...

### Pierrs massive discrete stocks

```{r Pierrs_Discretion, eval = F ,echo = T,warning = F,message = F}

Pierre <-  Clean_Results_Trans %>% 
  filter(Territory == "Saint Pierre & Miquelon (France)") %>% 
  left_join(Exploited_Species,
            by = "TaxonKey")

# Very wrong!
# using 600051 to see what's the problem with the Area index

# Found the problem, Territory and Neighbour were switched un the last step of the EstTransSpp function

### Côte de Ivory missing data

For some reason Côte de ivory is missing data. It was fixed at the beginning when I was averaging 1951 to 1961 instead of 2004 to 2014, but now is somehow back to zero.

```{Cote_Deivory, eval =F, echo =F}

# It might be a problem in the name côte de'ivory....
# Nope, both INDEX and neighbours datasets are names alike

# Run getSppDistribution function with this:
Model="All"
Coord=CoorG

# Spp <- 600423 #This species should work

# Its a problem with compabillity between Windows and MAC. Fixed by changing the neighbours csv. to excell

# Now Check Vietnam...Curacao and Réunion...
# In INDEXES "Vietnam" in all others "Viet Nam"
# Fixed directly on the excell

# The russioan probelmo

EEZCellIUD913 <- EEZ_CellID %>% 
  filter(EEZID == 913)

R912 <- Neighbours_Data %>% 
  filter(ID == 912)

R913 <- Neighbours_Data %>% 
  filter(ID == 913)

anti_join(R912,R913)

Index_Code913 <- Index_Code %>% 
  filter(EEZID == 913)

Neighbours_Data %>% 
  filter(INDEX %in% Index_Code913$INDEX)

# SAU relations between INDEX and Country's EEZs
EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
# EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_JEPA_92019.xlsx",sep=""))
EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
# EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_JEPA_92019.xlsx",sep=""))
colnames(EEZ_CellID) <- c("EEZID","INDEX")

# The path
path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
# #The File

fnam_world <- "SAUEEZ_July2015.shp"
World_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(Territory = Name)

x <- Neighbours_Data %>%
  select(-Neighbour) %>% 
  group_by(Territory) %>% 
  distinct() %>% 
  anti_join(Index_Code) %>% 
  group_by(Territory) %>% 
  summarise(n());x

# World_sf %>% 
#   filter(Territory %in% x$Territory)

# Fuck it! Re-run Neighbours code...

Russians <- c("Russia (Laptev to Chukchi Sea)", #913
              "US Virgin Islands") #912

SF_Names <- 850

Russian_Index <- Index_Code %>% 
  filter(Territory %in% Russians)

unique(Russian_Index$EEZID)
unique(Russian_Index$Territory)

World_sf %>% 
  # filter(Territory == "Russia (Laptev to Chukchi Sea)") # EEZid 912
  # filter(Territory == "Russia (Kara Sea)") # EEZid also 912
  filter(Territory %in% Russians) %>% 
  ggplot() +
  geom_sf(aes(fill = Territory))

unique(Russian_sf$Territory)

# split shapefile by DF
Russian_id <- World_sf %>% 
  filter(Territory %in% Russians) %>% 
  left_join(Russian_Index, by= "Territory") %>%  
  mutate(EEZID = ifelse(Territory == "Russia (Kara Sea)",912,913)) %>% 
  filter(EEZID == 913) %>% 
  st_simplify(preserveTopology = TRUE, dTolerance = 1000)

ggplot(Russian_id) +
  geom_sf(aes())

# ok!

# split shapefile by DF
Russia_id_912_913 <- World_sf %>% 
  filter(Territory %in% Russians) %>% 
  left_join(Russian_Index, by= "Territory") %>%  
  mutate(EEZID = ifelse(Territory == "Russia (Kara Sea)",912,913)) %>% 
  as.data.frame() %>% 
  ungroup() %>% 
  select(Territory,INDEX,EEZID)

write.csv(Russia_id_912_913,
          "Russia_id_912_913.csv",
          row.names = F)

head(x)

### Number of Collapsed USA species

```{r Collapsed_USA, eval = F ,echo = T,warning = F,message = F}

#  At the end, the ram legacy and the SAU are tide in results...

USA_Collapsed <- Species_Status %>% 
  filter(str_detect(Territory, pattern="USA")#,
         # Status == "Collapsed"
  ) %>% 
  ungroup() %>% 
  mutate(TaxonKey = as.numeric(TaxonKey)) %>%
  left_join(Exploited_Species)

# Comparring to RAM legacy in the W pacific coast

# Sabelfish match
# Pacifc sardine no data ram
# Chillipepper match
# Lincod no match althou circular path in RAM
# Dover no match by far...
# Chub mackerel... match
# Petral metch
# Black Rockfish No mach...ish
# Widow rockfish no match
# Starry flounder no match
# Rex sole no data RAM
# Pacific ocean percCollapsed Vs Overfished
#

### Fixing Russia Moneeeeey

```{r russia}

# Shapefile names
Russia_Sf <- World_land_sf %>% 
  filter(str_detect(fishing_entity,"Russia")) %>% 
  pull(fishing_entity)

"Russia"

Russia_Trans <- Revenue_Country %>% 
  filter(str_detect(fishing_entity,"Russia")) %>% 
  pull(fishing_entity)

"Russian Federation"
### Laptev and Chukchi are the issue, No Alaska'?

### Wake
Wake_ssf <- World_sf %>% 
  filter(str_detect(eez_name,"Wake")) %>% 
  pull(eez_name)

"Wake Isl. (USA)"

Wake_Trans <- Transboundary_Spp %>% 
  filter(str_detect(eez_name,"Wake")) %>% 
  pull(eez_name)

"NA"

Wake_Tresh <- Tresholded_T_Data %>% 
  filter(str_detect(eez_name,"Wake")) %>% 
  pull(eez_name)

"NA"

Wake_Raw <- Clean_Results_Trans %>% 
  filter(str_detect(eez_name,"Wake"))

#### Son todas under 25%.... Por eso

#### Macquarie Island
Macquarie_Raw <- Clean_Results_Trans %>% 
  filter(str_detect(eez_name,"Macquarie"))

# Under 25% Bye

### Minomi

Neighbours_Data %>% 
  filter(str_detect(Territory,"Japan")) %>% 
  pull(Territory) %>% 
  unique()

# Not in our shaopefile

### UN Data exploration

```{r}

UN_Regions %>% 
  filter(fishing_entity %in% Clean_sau_eez_fes$fishing_entity) %>% 
  group_by(sub_region) %>% 
  summarise(n_countries = length(unique(fishing_entity))) %>% 
  arrange(n_countries)

World_sf %>% 
  as.data.frame() %>% 
  left_join(Clean_sau_eez_fes) %>% 
  left_join(UN_Regions) %>% 
  filter(fishing_entity %in% Clean_sau_eez_fes$fishing_entity) %>% 
  group_by(sub_region) %>% 
  summarise(Size_EEZ = sum(Area_km2)) %>% 
  arrange(desc(Size_EEZ))

# Extra Analysis
## Extra Analysis; Functions

```{r Trans_Spp_Function_All, eval = F ,echo = T,warning = F,message = F}

# Function to determine whether or not a species is transboundary for each model

#### For testing 
# Spp <- 600059
# Model <- "All"
# Neighbours <- Neighbour_List
# Coord = CoorG
# __________________________________

# The function
EstTransIndex <- function(Spp,Model,Neighbours,Coord,Save="Y"){

  #____________ ESTIMATING MODEL INDEX (TRESHOLD 1)_________ #
  Trans_Spp <- SppDist %>%
    filter(INDEX %in% Neighbours$INDEX,# Filter data only located within EEZs
           Model != "SAU_C") %>% # Only using observational and modelled data
    mutate(Value = ifelse(Value > 0, 1,0)) %>%
    left_join(EEZ_CellID,
              by = "INDEX") %>% 
    left_join(EEZIDs_List,
              by = "EEZID")

  # MODEL INDEX (TRESHOLDS 1 & 2) #
  Model_Index_D <- Trans_Spp %>% 
    group_by(Name,
             TaxonKey,
             Model
    ) %>% 
    summarise(n_cells_spp = n()) %>% 
    select(-n_cells_spp)

  #Step 1.  Get EEZ id and Neighbour
  Neighbours_EEZ <- Neighbours %>% 
    group_by(EEZID,Country_Territory,Neighbour_Territory) %>% 
    summarise(n=n()) %>% 
    ungroup() %>% 
    select(-n)

  # Step 2. Determines the amount of grids present in each country
  Spp_Grid <- Trans_Spp %>% 
    group_by(TaxonKey,
             Model, 
             EEZID) %>% 
    summarise(n_spp_eez = length(unique(INDEX))) %>% 
    left_join(Neighbours_EEZ,
              by = "EEZID") %>% 
    filter(Country_Territory %in% Trans_Spp$Name, #Filter out unwanted Neighbours (those who don't have grids within but get included because they are Neighbours)
           Neighbour_Territory %in% Trans_Spp$Name)

  # Step 3. Sum total grids per Neighbours

  # Split dataframes to merge latter
  Country_Territory_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      Model_Index, # Un-comment after producing models x datasets
      TaxonKey,Name=Country_Territory,n_spp_eez
    )

  Neighbour_Territory_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      Model_Index,
      TaxonKey,n_spp_eez,Name=Neighbour_Territory, Country_Territory
    )

  # Merge dataframes to get totals per Neighbourds
  Area_Index_D <- full_join(Country_Territory_T,
                            Neighbour_Territory_T, by = c("Name","TaxonKey","Model")) %>%
    rowwise() %>%
    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
    distinct() %>% # Removes false duplicates from `full_join()`
    rename(Neighbour_Territory = Name,
           n_spp_Country = n_spp_eez.x,
           n_spp_Neighbour = n_spp_eez.y) %>% 
    mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
    select(1:4,6,8)

  #____________ FINAL INDEX TABLE_________ #
  Indexes <- Model_Index_D %>% 
    rename(Country_Territory = Name) %>% 
    full_join(Area_Index_D,
              by = c("TaxonKey","Country_Territory","Model")
    ) %>% 
    filter(!is.na(Area_Index))%>%  # Remove cases where the country does not pass the area_index and viceversa
    select(Model,TaxonKey,Country_Territory,Neighbour_Territory,everything())

    File_Name <- paste(Spp,"_Transboundary.csv",sep = "")
    Save_Path <- paste(Results_Path,"All_Models/",File_Name,sep="")

    write.csv(Indexes,
              Save_Path,
              row.names = F)

  if(nrow(Indexes) == 0 & Save == "Y"){

    # Reads dataset of Non transboundary species
    Non_Transboundary_Data <- fread(paste(Results_Path,"All_Models/","Non_Transboundary_Data.csv",sep=""))

    # Get current Spp that is not transboundary 
    Current_Spp <- tibble(Non_trans = Spp)

    # Set a name for file and saves data
    New_Non_Name <- paste(Results_Path,"All_Models/","Non_Transboundary_Data.csv",sep="")
    write.csv(New_Non, New_Non_Name, row.names = F)

  ### Function return

  EstTransIndex=Indexes # A dataframe with

### Testing Function ####
# Spp <- 600006
# Model <- "All"
# Neighbours <- Neighbour_List
# 
# Tryout <- EstTransIndex(Spp,Model,Neighbours,CoorG,Save="N")
# 
# Over_20 <-Tryout %>% 
#     filter(Area_Index > 0.20,
#            Area_Index < 0.80)

# Spp <- NULL
# Model <- NULL

## Extra Analysis; Results

### Maps for each model/data-set
```{Tran_country_Map_All, eval =F, echo =F}

World_EEZs_simple <- World_EEZs %>%
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
  left_join(TenTwenyfive, by ="Name") #%>%
# filter(!is.na(n_trans)) #%>%
# st_transform(crs = 3832)

# head(World_EEZs_simple)
# World_EEZs_simple %>% 
#   filter(Name == "Chile")

pal <- wes_palette("Zissou1", 100, type = "continuous")

Mod <- unique(TenTwenyfive$Model)

# Loop through all variables
for(v in 1:length(Mod)){

  Model_List <- Mod[v]

  plot <- ggplot(data = subset(World_EEZs_simple,Model %in% Model_List)) +
    geom_sf(aes(fill = n_trans)) +
    scale_fill_gradientn(colours = pal,
                         na.value = "white") +
    ggtheme_map() +
    ggtitle(paste(Model_List))

  # Name plot
  Plot_Name <- paste(Model_List,"plot.png",sep="_")

  # Save plot
  ggsave(
    plot = plot,
    width = 14,
    height = 10,
    units = "in",
    filename = Plot_Name,
    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/All_Models/"
  )

```{r Continent_PNG, eval =F }

names(UN_Regions)
# Load Land shapefile
path_world_land <- paste(Data_Path,"Spatial_Data/ne_50m_admin_0_countries",sep="")
# #The File
fnam_world_land <- "ne_50m_admin_0_countries.shp"

World_land_sf <- st_read(dsn = path_world_land,
                         layer =file_path_sans_ext(fnam_world_land)) %>% 
  st_transform(crs = 4326)

head(World_land_sf)

Regions <- unique(World_land_sf$REGION_UN)
# r= 1

for(r in 1:length(Regions)){

  Oceania <- World_land_sf %>%
    st_transform(crs = 3832)

  Oceania %>% 
    filter(REGION_UN %in% Regions[5]) %>% 
    ggplot() +
    geom_sf(aes(),fill="black",colour = "black") +
    ggtheme_map() #+
  # coord_sf(xlim = c(-180, 90), ylim = c(-90, 90), expand = FALSE)

  Plot_Name <-paste(Regions[5],".png",sep="")

  ggsave(Plot_Name,
         plot = last_plot(),
         width = 4,
         height = 4,
         units = "in",
         path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Images_Data/"
  )

```{r round_map, eval = F, echo = F}
# #### Round map tryout

# ### EEZ shapefile
# eez  = readRDS(paste(Data_Path,"Spatial_Data/eez_simplified.rds",sep="")) #taken from cotterel https://github.com/cottrellr/shocks
# 
# eez = spTransform(eez, CRS("+proj=longlat"))
# eez = spTransform(eez, CRS("+proj=wintri"))
# eez = fortify(eez) 
# 
# World_sf_si <- World_sf %>%
#   st_transform(crs = 4326
#

# mapworld = fortify(spTransform(rworldmap::getMap(), CRS("+proj=wintri")))
# 
# mapworld<- mapworld %>% 
#   rename(Territory = id) %>% 
#   left_join(Data,
#             by = "Territory") %>% 
#   left_join(Data_EEZ,
#             by = "Territory") %>% 
#   rename(id = Territory)
# 
# # head(mapworld)
# 
# #create map boundary
# ll.to.wt <- function (points)
#   as.data.frame(spTransform(SpatialPoints(points, CRS("+proj=longlat")),
#                             CRS("+proj=wintri")))
#  
# lseq = seq(-85, 85, by=.25)
# boundary <- ll.to.wt(data.frame(
#   long = c(rep(-180, length(lseq)), rep(180, length(lseq)), -180),
#   lat  = c(lseq,                    rev(lseq),          lseq[1])))
#  
# # New facet label names for dose variable
# ggplot()+
#   geom_polygon(data=boundary, aes(x=long, y=lat), fill="azure") +
#   geom_map(data=mapworld, map=mapworld, aes(map_id=id, x=long, y=lat), fill ="gray93", colour=NA) +
#   geom_polygon(data = mapworld, 
#                aes(
#                  x = long,
#                  y = lat,
#                  group = group,
#                  fill = BinsLan
#                ),
#                colour="grey") +
#   geom_polygon(data = mapworld, 
#                aes(
#                  x = long,
#                  y = lat,
#                  group = group,
#                  fill = Bins)
#                ) +
#   geom_path(data=eez, aes(x=long,y=lat, group=group),colour="grey") +
# geom_point(data=ui, aes(x=long, y=lat, size=M, color=M), alpha=0.9) +
# geom_text_repel(data=ui,aes(x=long, y=lat, label=un.name), size=2.5, color = 'black',
#                 box.padding = unit(0.5, "lines"),
#                 point.padding = unit(0.5, "lines"),
#                 segment.color = 'grey50') +
# scale_radius(range = c(1, 2)) #+
# scale_colour_distiller(palette ="Spectral", direction = 1, limits=c(0,1), breaks=c(c(0,1))) + # or direction=1
# theme_map()+
#   theme(legend.key = element_blank(),
#         strip.background = element_blank(),
#         legend.position = "none",
#         text = element_text(size=12,face="bold"))+
#   facet_wrap(~variable, scales = "free", ncol=1)+scale_shape(guide=FALSE)+scale_size(guide=FALSE)
# y=tag_facet(q, tag_pool = c("d","e","f"))

# Vulnerability Assessment

```{r Vulnerabillity, eval = T, echo = F}

>>>>

## Determine Catch Trends

@@

Categories are:

- Increasing Catch 
- COnstant Catch
- Decreasing Catch

@@

# Percentage species analyzed from the identified species
936/length(unique(SAU_Global_Data$taxon_key)) # 67.5

@@

# Read SAU non-reconstructed catch data from 2006 for comparrisonwith Sumaila
# Provided by Vicky Lam
SAU_FAO_Data <- fread(paste(my_path("D"),"Distribution/LVCatch_byYrEEZFETaxa_2005_09.csv", sep ="")) %>% 
  filter(#eezid != 0,
         year == 2006) %>%
  group_by(fishing_entity_id,taxon_key,eezid) %>% 
  summarise_at(c("sumcatch"),
               sum,na.rm=T)

@@

### Non-shared Transboundary

@@

@@

### Data For Map (Fig. 1)

@@

### Map of Transboundary Species

@@

````

### Plot weighted bars

```{r, eval = T, echo = F}
  Rev_Plot <- ggplot(
    # Regional plots
    data = Subregion_Rev_Data,
    aes(
      x=reorder(id,Value_sum),
      y=Value_sum, 
      fill=Value_sum
    )
  ) +    
    ylim(-5, 30) +
    geom_bar(stat="identity") +
    # Regional averages
    geom_point(data = Subregion_Rev_Data,
               aes(
                 x=reorder(id,Value_sum),
                 y=Value_m
               ),
               colour = "black",
               alpha = 0.5,
               size = 0.5
    ) +
    # Regional sds
    geom_errorbar(data = Subregion_Rev_Data,
                  aes(
                    ymin=ifelse(Value_m-Value_sd <= 0,0,Value_m-Value_sd), # sets lower to 0
                    ymax=Value_m+Value_sd
                  ), 
                  width=.2,
                  position=position_dodge(.9),
                  alpha = 0.5) +
    # Looking good
    theme_minimal(base_size = 9) +
    theme(
      legend.key.width =unit(1,"line"),
      legend.key.height =unit(0.9,"line"),
      legend.position = c(0.86,0.55),
      axis.text = element_blank(),
      axis.title = element_blank(),
      panel.grid = element_blank(),
      plot.margin = margin(1,0,0,-2.5,"cm") # top,x,x,left
      # plot.margin = margin(0,-10,-6,-10,"cm")
    )  +
  coord_polar(start = 0) + 
  geom_text(data=label_data_rev, 
            aes(x=id,
                # y=ifelse(sub_region=="N. Europe",250,Value_sum+1), # Fix names overlap
                y = Value_sum,
                label=sub_region,
                hjust=hjust), 
            color="black",
            fontface="bold",
            size=2, 
            angle= label_data_rev$angleb, 
            inherit.aes = FALSE) +
    scale_fill_gradientn("",
                         colours = pal,
                         limits = c(0,30),
                         breaks = seq(0,30,6)
                         ) + # puts legend text on the left
    guides(fill = guide_colorbar(label.position = "left"));Rev_Plot

@@

## OHI-Territories

@@

### Mackerel conflict

@@

### OHI-Species

@@
